Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-20 paper/sec-pineappl.tex
Fix wrongly defined xiR and xiF

Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R}^2 / Q^2$ and $\xi_\mathrm{F} = \mu_\mathrm{F}^2 / Q^2$,
\begin{multline}
\frac{\mathrm{d} \sigma_{ab}}{\mathrm{d} \mathcal{O}} (x_1, x_2, \mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{F}) \\
= \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R} Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R} ) \log^n ( \xi_\mathrm{F} ) W_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \mathcal{O} \right) \text{.}
\label{eq:expansion}
\end{multline}
The cross section shown above is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft- and collinear safety, etc.).

@@

Using eq.~\eqref{eq:expansion} and
\begin{multline}
\frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{R}) \\
= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F} Q^2) f_b (x_2, \xi_\mathrm{F} Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
\label{eq:pineappl-convolution}
\end{multline}
\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.

@@

To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO (with some arguments suppressed for the phase-space weights):
\begin{equation}
\begin{split}
\sigma_{ab}
    &= \alpha^2 W_{ab}^{(0,2,0,0)} \\
    &+ \alphas \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R} Q^2 \right) \log (\xi_\mathrm{F}) \alpha^2 W_{ab}^{(1,2,0,1)} \\
    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}) \alpha^3 W_{ab}^{(0,3,0,1)} \text{.}
\end{split}
\end{equation}
The first term with index $(0,2,0,0)$ is the LO term, the following line shows the NLO QCD correction, and the final line the NLO EW correction.
Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
At NLO these terms are not present for this process so that terms proportional to $\log (\xi_\mathrm{R})$ vanish.
Both NLOs, however, have contributions from a collinear counterterm that depends on the factorisation scale.

@@

%\subsubsection{Example: top-pair production}
%
%\begin{equation}
%\begin{split}
%\sigma_{ab}
%&= \alpha^2                                                                   W_{ab}^{(0,2,0,0)}
% + \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha                         W_{ab}^{(1,1,0,0)}
% + \alphas^2 \left( \xi_\mathrm{R} Q^2 \right)                                W_{ab}^{(2,0,0,0)} \\
%&+ \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)                                W_{ab}^{(3,0,0,0)} \\
%&+ \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)          \log (\xi_\mathrm{F}) W_{ab}^{(3,0,0,1)} (Q^2)
% + \alphas^3 \left( \xi_\mathrm{R} Q^2 \right)          \log (\xi_\mathrm{R}) W_{ab}^{(3,0,1,0)} (Q^2) \\
%&+ \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha                         W_{ab}^{(2,1,0,0)} \\
%&+ \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha   \log (\xi_\mathrm{F}) W_{ab}^{(2,1,0,1)} (Q^2)
% + \alphas^2 \left( \xi_\mathrm{R} Q^2 \right) \alpha   \log (\xi_\mathrm{R}) W_{ab}^{(2,1,1,0)} (Q^2) \\
%&+ \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2                       W_{ab}^{(1,2,0,0)} \\
%&+ \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 \log (\xi_\mathrm{F}) W_{ab}^{(1,2,0,1)} (Q^2)
% + \alphas   \left( \xi_\mathrm{R} Q^2 \right) \alpha^2 \log (\xi_\mathrm{R}) W_{ab}^{(1,2,1,0)} (Q^2) \\
%&+           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3                       W_{ab}^{(0,3,0,0)} \\
%&+           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3 \log (\xi_\mathrm{F}) W_{ab}^{(0,3,0,1)} (Q^2)
% +           \left( \xi_\mathrm{R} Q^2 \right) \alpha^3 \log (\xi_\mathrm{R}) W_{ab}^{(0,3,1,0)} (Q^2)
%\end{split}
%\end{equation}

>>>>

Fixed-order partonic cross sections $a + b \to X$ supported by \textsc{PineAPPL} are expansions in powers of the strong coupling $\alphas$, the electromagnetic coupling $\alpha$, and the logarithms of $\xi_\mathrm{R} = \mu_\mathrm{R} / Q$ and $\xi_\mathrm{F} = \mu_\mathrm{F} / Q$,
\begin{multline}
\frac{\mathrm{d} \sigma_{ab}}{\mathrm{d} \mathcal{O}} (x_1, x_2, \mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{F}) \\
= \sum_{k,l,m,n} \alphas^k \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^l \log^m ( \xi_\mathrm{R}^2 ) \log^n ( \xi_\mathrm{F}^2 ) W_{ab}^{(k,l,m,n)} \left( x_1, x_2, Q^2, \mathcal{O} \right) \text{.}
\label{eq:expansion}
\end{multline}
The cross section shown above is differential w.r.t.\ the observable $\mathcal{O}$, which, in general, is a function of phase space and subject to the usual conditions (soft- and collinear safety, etc.).

@@

Using eq.~\eqref{eq:expansion} and
\begin{multline}
\frac{\mathrm{d} \sigma}{\mathrm{d} \mathcal{O}} (\mathcal{O}, \xi_\mathrm{R}, \xi_\mathrm{R}) \\
= \sum_{a,b} \int_0^1 \mathrm{d} x_1 \int_0^1 \mathrm{d} x_2 \int_{Q^2_\mathrm{min}}^{Q^2_\mathrm{max}} \mathrm{d} Q^2 \, f_a (x_1, \xi_\mathrm{F}^2 Q^2) f_b (x_2, \xi_\mathrm{F}^2 Q^2) \sigma_{ab} (x_1, x_2, Q^2, \xi_\mathrm{R}, \xi_\mathrm{R}) \text{,}
\label{eq:pineappl-convolution}
\end{multline}
\textsc{PineAPPL} can then quickly calculate hadronic cross sections for arbitrarily many PDF sets and perform scale variations.

@@

To give an example of eq.~\eqref{eq:expansion}, the following shows Drell--Yan lepton-pair production up to terms at NLO (with some arguments suppressed for the phase-space weights):
\begin{equation}
\begin{split}
\sigma_{ab}
    &= \alpha^2 W_{ab}^{(0,2,0,0)} \\
    &+ \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 W_{ab}^{(1,2,0,0)} (Q^2) + \alphas \left( \xi_\mathrm{R}^2 Q^2 \right) \log (\xi_\mathrm{F}^2) \alpha^2 W_{ab}^{(1,2,0,1)} \\
    &+ \alpha^3 W_{ab}^{(0,3,0,0)} (Q^2) + \log (\xi_\mathrm{F}^2) \alpha^3 W_{ab}^{(0,3,0,1)} \text{.}
\end{split}
\end{equation}
The first term with index $(0,2,0,0)$ is the LO term, the following line shows the NLO QCD correction, and the final line the NLO EW correction.
Note that all terms depend on the renormalisation scale only indirectly through $\alphas$, because 1) higher-order terms in $\alpha$ never generate a renormalisation scale dependence (in the $\alpha$ schemes that are valid according to section~\ref{sec:multi-coupling-expansion}) and 2) higher-order QCD corrections only introduce an explicit renormalisation scale dependence in counterterms with vertices with more than two gluons.
At NLO these terms are not present for this process so that terms proportional to $\log (\xi_\mathrm{R}^2)$ vanish.
Both NLOs, however, have contributions from a collinear counterterm that depends on the factorisation scale.

@@

%\subsubsection{Example: top-pair production}
%
%\begin{equation}
%\begin{split}
%\sigma_{ab}
%&= \alpha^2                                                                       W_{ab}^{(0,2,0,0)}
% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(1,1,0,0)}
% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(2,0,0,0)} \\
%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(3,0,0,0)} \\
%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{F}^2) W_{ab}^{(3,0,0,1)} (Q^2)
% + \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{R}^2) W_{ab}^{(3,0,1,0)} (Q^2) \\
%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(2,1,0,0)} \\
%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{F}^2) W_{ab}^{(2,1,0,1)} (Q^2)
% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{R}^2) W_{ab}^{(2,1,1,0)} (Q^2) \\
%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2                         W_{ab}^{(1,2,0,0)} \\
%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{F}^2) W_{ab}^{(1,2,0,1)} (Q^2)
% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{R}^2) W_{ab}^{(1,2,1,0)} (Q^2) \\
%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3                         W_{ab}^{(0,3,0,0)} \\
%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{F}^2) W_{ab}^{(0,3,0,1)} (Q^2)
% +           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{R}^2) W_{ab}^{(0,3,1,0)} (Q^2)
%\end{split}
%\end{equation}
